% LaTeX resume using res.cls
\documentclass[margin]{res}
\headsep=0pt
\headheight=0pt
\topmargin=-40pt

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[pdftex,
        colorlinks=true,
        urlcolor=rltblue,       % \href{...}{...} external (URL)
        filecolor=rltgreen,     % \href{...} local file
        linkcolor=rltred,       % \ref{...} and \pageref{...}
        pdftitle={Jason Pope's Resume},
        pdfauthor={Jason G Pope},
        pdfsubject={Resume},
        pdfkeywords={Jason Pope},
        pdfproducer={pdfLaTeX},
        pagebackref,
        pdfpagemode=None,
        bookmarksopen=true]{hyperref}

\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

\setlength{\headheight}{.5pt}
% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\Large\bf Jason G. Pope}
% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\moveleft.5\hoffset\centerline{jgpope@gmail.com}
\moveleft.5\hoffset\centerline{(818) 497-2079}


\begin{resume}
               
\section{TECHNICAL \\ SKILLS}
{\sl Languages} \parskip 2pt
\begin{itemize} \itemsep -2pt
  \item[]{\emph{Proficient:} Python, Ruby}
  \item[]{\emph{Familiar:} C, C++, x86, PHP, Perl, Javascript, Java}
\end{itemize}

{\sl Tools, Systems and Platforms}
\begin{itemize}
  \item[]{Linux, Rails, Flask, Django, PostgreSQL, MySQL, Mongo, Redis, AWS}
\end{itemize}
        
\section{EXPERIENCE} \parskip 10pt

{\sl Data Privacy Engineer} \hfill August 2022 to Present \\
Apple Inc, San Diego, CA
\begin{itemize} \itemsep -2pt
  \item Data Privacy in Video Engineering 
\end{itemize}

{\sl Head of Engineering and Chief Architect} \hfill July 2015 to August 2022 \\
Seclytics, San Diego, CA
\begin{itemize} \itemsep -2pt
  \item Leveraging our industry knowledge and expertise we built Seclytics from the ground up. 
  \item Designed and built the Seclytics API and dashboard providing predictive threat intelligence using machine learning.
  \item Worked with customers and leads to provide solutions for their business needs.
\end{itemize}

{\sl Senior Software Engineer} \hfill September 2009 to July 2015 \\
Websense Security Labs, Websense Inc (Forcepoint) San Diego, CA
\begin{itemize} \itemsep -2pt
  \item Developed the first security application for Facebook pages. This ultimately lead to Facebook using Websense for URL filtering.
  \item Worked closely with security researchers to create infrastructure and products to help identify malicious actors.
  \item Created Websense's Android security software with an innovative ''self-terminating'' VPN.
  \item Researched and built an internal threat intelligence platform by connecting our global threat data from web, email and file sandboxes.
\end{itemize}

{\sl Consultant} \hfill  June 2003 to 2012 \\
Log Base Two, sole proprietorship
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Created an API for one of the top iPhone Navigation Apps.
  \item Developed custom Java field management and accounting software for a private investigation firm in LA.
\end{itemize}
        
{\sl Software Engineer} \hfill  January 2009 to April 2009 \\
Xandros Inc (Linspire), San Diego, CA
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Package manager for CNR (Click-n-run) Debian repositories.
\end{itemize}

\section{AWARDS}
\begin{itemize} \itemsep -2pt
  \item[2013]{Innovator of The Year at Websense}
  \item[2012]{Innovator of The Year at Websense}
  \item[2011]{Foursquare Hackathon Winner}
  \item[2010]{Innovative Product of The Year at Websense}
  \item[2009]{Yahoo Open Hack Day NYC, best hack for accessibility} 
  \item[2008]{Yahoo HackU UCSD, best overall hack}
\end{itemize}
\section{EDUCATION} {\sl Bachelor of Science, Computer Science}\\
        University of California: Davis, June 2009\\

\end{resume}
% \moveleft.5\hoffset\centerline{\emph{References available on request}}
\end{document}
